---
title: "Lab 3 : COVID-19"
subtitle: 'Ecosystem Science and Sustainability 330'
author: 
  - name: Stephanie Farmer 
  - email: stephgf@colostate.edu
format: html
editor: visual
execute: 
  echo: true 
---
```{r}
library(tidyverse)
library(flextable)
library(zoo)
```
##Question 1 :How does easy access to historical and real-time environmental data shape our understanding of climate trends, resource management, and public health? What happens when this data disappears or becomes inaccessible? The role of independent archiving and collaborative stewardship has never been more critical in ensuring scientific progress and accountability.

Easy access to historical and real-time environmental data is crucial for understanding climate trends, managing natural resources, and protecting public health. Without this access, scientists and policymakers would struggle to monitor environmental changes and identify patterns that reveal long-term climate trends. In resource management, data is essential for predicting ecological responses and helping communities develop effective adaptation and mitigation strategies. Similarly, in public health, real-time data enables rapid responses to disease outbreaks and emerging health risks. By maintaining accessible and reliable environmental data, we can make informed decisions that support sustainability, resilience, and public well-being. Without this data we will lose important scientific progress and hinder further research. Ensuring continuous access to reliable environmental data is essential for informed decision making, sustainability, and the protection of bothe ecosystems and public health.

```{r}
data = read.csv('https://raw.githubusercontent.com/nytimes/covid-19-data/master/us-counties.csv')
```

#Question 2: Daily Summary 
```{r}
my.date <- as.Date("2022-02-01")
my.state <- "Colorado"
```

```{r}
library(dplyr)

```

